---
title: "Color me honest!"
author:
  - name: Carina I. Hausladen
    orcid: 0000-0003-4397-2339
    email: carinah@caltech.edu
    affiliations:
      - name: California Institute of Technology
        address: California Blv
        city: Pasadena
        state: CA
date: "`r format(Sys.time(), '%d %B, %Y')`"
format:
  html:
    toc: true
    html-math-method: katex
---

# Setup 
```{r setup, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
rm(list=ls())

library(readr)
library(reshape2)
library(mousetrap)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)
library(ggdist)
library(purrr)
library(gt)
library(grid)
library(gridExtra)


read.csv("/Users/carinah/Documents/GitHub/color-me-honest/data/nov_2018.csv") %>%
  mutate(across(c(player.checkmore), ~1-.)) ->raw_nov
read.csv("/Users/carinah/Documents/GitHub/color-me-honest/data/jun_2019.csv") %>%
  filter(session.is_demo == 0, session.code != 'ty94co6a') %>%  #dropping demo and early test sessions
  mutate(across(c(player.checkmore, player.cblind), ~1-.)) ->raw_jun # both values need to be flipped
names<-intersect(colnames(raw_jun), colnames(raw_nov))

rbind(raw_nov[,colnames(raw_nov) %in% names],
             raw_jun[,colnames(raw_jun) %in% names]) %>%
  filter(player.cblind == 0 | is.na(player.cblind),  #color-blind (3)
         player.report != "R")->df #exclude failed to report in time (3)	

df$treatment<- ifelse(df$player.treat_color==1 & df$player.treat_pressure==1, "C*", 
                      ifelse(df$player.treat_color==1 & df$player.treat_pressure==0, "C", 
                             ifelse(df$player.treat_color==0 & df$player.treat_pressure==1, "R*",
                                    ifelse(df$player.treat_color==0 & df$player.treat_pressure==0, "R", "NA"))))


rbind(read.csv("/Users/carinah/Documents/GitHub/color-me-honest/data/TimeSpent_jun_2019.csv"),  
      read.csv("/Users/carinah/Documents/GitHub/color-me-honest/data/TimeSpent_nov_2018.csv"))  %>%
  filter(page_name=="Decision") %>%
  select(participant__code, seconds_on_page) %>%
  na.omit()->df_time

df_time <- df_time[df_time$participant__code %in% df$participant.code, ]
colnames(df_time)<-c("participant.code","seconds_on_page")


df %>% left_join(df_time, by=c("participant.code")) ->df

source("utils.R")
rm(df_time)
```

```{r mt df, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
df_lng <- data.frame()
for (i in 1:length(df$participant.code)) {
  df_temp <- data.frame(participant.code=df$participant.code[i],
                        treatment=df$treatment[i],
                        report=df$player.report_value[i],
                        sec_op=df$seconds_on_page[i],
                        x = as.numeric(unlist(strsplit(as.character(df$player.mouse_x[i]),split = ","))), 
                        y = as.numeric(unlist(strsplit(as.character(df$player.mouse_y[i]),split = ","))),
                        t = as.numeric(unlist(strsplit(as.character(df$player.mouse_t[i]),split = ","))) 
                        )
  df_lng <- rbind(df_lng, df_temp)
}

#df_lng %>% write.csv("df_lng.csv")
rm(df_temp)
```

```{r calc total dist, echo=FALSE, cache=TRUE}
df_lng %>%
  group_by(participant.code) %>%
  mutate(x_diff = lead(x) - x, 
         y_diff = lead(y) - y) %>%
  slice(-n()) %>%
  mutate(distance = map2_dbl(x_diff, y_diff, ~ sqrt(.x^2 + .y^2))) %>%
  summarise(total_distance = sum(distance)) %>%
  ungroup() %>%
  mutate(total_distance = as.numeric(total_distance))->total_dist
#total_dist %>% write_csv("totaldist.csv")
# the author then codes based on the plotted trajectories 1) A/O types 2) nr. options visited
```

# Overview
```{r overview, cache=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
females<-round(table(df$player.sex)[1]/sum(table(df$player.sex))*100, digits=0)
mjor<-round(table(df$player.mjr)[1]+table(df$player.mjr)[2]/sum(table(df$player.mjr))*100, digits=0)
age<-round(mean(df$player.age), digits=1)
sd<-round(sd(df$player.age), digits=1)
```

In a preregistered\footnote{\url{https://doi.org/10.1257/rct.3115-2.1}} laboratory experiment, we collected a total of `r dim(df)[1]` observations (between 55 and 58 in each condition, excluding color-blind participants and those who failed to report in time in the time pressure conditions). 
The data sample contains `r females` \% females,`r mjor` \%  business administration and economics students. The average age is `r age` years (SD = `r sd`). 

A manipulation check confirms that \RP{} and \CP{} participants reported significantly higher levels of perceived pressure than their counterparts in conditions \R{} and \C{} (@tbl-A1).


# Time pressure effect depends on the die

::: columns
::: column
```{r Fig 2A ttests, cache=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
df %>%
  select(treatment, player.report_value) %>%
  do(pairwise_tests = tidy(pairwise.t.test(.$player.report_value, .$treatment, p.adj = "none"))) %>%
  unnest(pairwise_tests) %>%
  mutate(p.value = map_pvalue(p.value)) %>%
  filter(!p.value == "ns") -> ttest_all

ttest1<-t.test(player.report_value~treatment, 
               data=df%>% filter(treatment=="R*"|treatment=="R"), 
               alternative="two.sided") 
ttest2<-t.test(player.report_value~treatment, data=df%>% filter(treatment=="R"|treatment=="C"), alternative="two.sided")

df %>%
  select(treatment, player.report_value) %>%
  group_by(treatment) %>%
  do(t_test = tidy(t.test(.$player.report_value, mu = 3.5))) %>%
  ungroup() %>%
  unnest(t_test) %>%
  select(treatment, estimate, statistic, p.value) %>%
  mutate(signif = map_pvalue(p.value)) %>%
  filter(!signif=="ns")->ttest3.5
```

We never observe an average die roll report below the `honesty reference' of 3.5 (@fig-2A).
In particular, there is evidence of dishonest behavior in conditions $C$ (t= `r round(ttest3.5[1,3], digits=1)`, pval=`r round(ttest3.5[1,4], digits=3)`) and  $R*$ (t= `r round(ttest3.5[2,3], digits=1)`, pval=`r round(ttest3.5[2,4], digits=3)`).
In line with our conjecture outlined in the introduction, we find the effect of time pressure to depend on the type of the die used. There is more dishonesty under time pressure with the regular die (t= `r round(ttest2$statistic, digits=1)`, pval=`r round(ttest2$p.value, digits=3)`) but no such effect can be found with the color die. 
Also note that without any time pressure, the use of the color die results in higher reports (t= `r round(ttest1$statistic, digits=1)`, pval=`r round(ttest1$p.value, digits=3)`).
These findings are corroborated by an ordered logit regression estimated using Bayesian inference.
:::

::: column
```{r Fig 2A, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
#| fig-cap: "Reported values by treatment group. The dashed horizontal lines show the full honesty benchmark. The dashed vertical line shows the mean reported value by treatment group."
#| label: fig-2A
df_counts <- df %>% 
  group_by(treatment) %>% 
  mutate(mean=mean(player.report_value)) %>%
  group_by(treatment, player.report_value, mean) %>% 
  summarize(count=n()) %>%
  group_by(treatment) %>%
  mutate(prob=count/sum(count))

p1<-as.character(ttest_all[2,3])
p2<-as.character(ttest_all[1,3])

ggplot(df_counts, aes(y = player.report_value, 
                      x = prob, 
                      group = treatment)) +
  geom_segment(aes(y = player.report_value, 
                   yend = player.report_value, 
                   x = 0, 
                   xend = prob),
               color = "grey", size = 0.8) +
  facet_wrap(~treatment, ncol=2)+
  theme_classic()+
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        text=element_text(size=9),
        aspect.ratio = 1)+
  scale_y_continuous(name="Reported Value", limits=c(1, 6), breaks = 1:6) +
  xlab("Treatment")+
  geom_hline(aes(yintercept = mean, color=treatment), size=.5) +
  
  geom_label(data = df_counts %>% select(treatment, mean) %>% unique(), 
            aes(x = 0, y = mean,
                fill=factor(treatment),
                label= paste('mu', "==", round(mean, digits=2))),
            parse = TRUE,
            hjust = -.0001, 
           color="white", fontface="bold",
            size = 3, 
            vjust = -.1) +

  labs(y = "Treatment", x = "Probability", color = "Player Report Value")+
  
  scale_x_continuous(name="Probability", limits=c(0, 0.3), breaks = c(0, 1/6, 0.3), labels = c(0,0.16,0.30)) +
  geom_hline(aes(yintercept = 3.5), size=.2, color="grey", linetype="dotted")+
  
  geom_vline(aes(xintercept = 1/6), size=.2, linetype="dotted", color="grey")+
  ###   
  geom_text(data = subset(df_counts, treatment == "C"),
            aes(x = unique(df_counts$prob[df_counts$treatment=="C" & df_counts$player.report_value==4])+.03, 
                y = unique(df_counts$mean[df_counts$treatment=="C"])-.1), label = ttest3.5$signif[ttest3.5$treatment=="C"], angle=90, color="grey", size=3, , vjust=.5, hjust=1.8)+
  geom_segment(data = subset(df_counts, treatment == "C"),
               aes(x = unique(df_counts$prob[df_counts$treatment=="C" & df_counts$player.report_value==4])+.03, 
                   xend = unique(df_counts$prob[df_counts$treatment=="C" & df_counts$player.report_value==4])+.03,
                   y = 3.5, 
                   yend = unique(df_counts$mean[df_counts$treatment=="C"])), 
               color = "grey", size = .5) +

### 
geom_text(data = subset(df_counts, treatment == "R*"),
          aes(x = unique(df_counts$prob[df_counts$treatment=="R*" & df_counts$player.report_value==4])+.03, 
              y = unique(df_counts$mean[df_counts$treatment=="R*"]-.11)), 
          label = ttest3.5$signif[ttest3.5$treatment=="R*"], angle=90, color="grey", size=3, vjust=.5, hjust=1.8)+
  
  geom_segment(data = subset(df_counts, treatment == "R*"),
               aes(x = unique(df_counts$prob[df_counts$treatment=="R*" & df_counts$player.report_value==4])+.03, 
                   xend = unique(df_counts$prob[df_counts$treatment=="R*" & df_counts$player.report_value==4])+.03,
                   y = 3.5, yend = unique(df_counts$mean[df_counts$treatment=="R*"])), 
               color = "grey", size = .5) +

  ### 
  geom_text(data = subset(df_counts, treatment == "R"),
            aes(x = .19,
                y = unique(df_counts$mean[df_counts$treatment=="R*"])-.17), 
            label = p1, angle=90, color="darkgrey", size=3, vjust=.5, hjust=1.8) +
  
  
  geom_segment(data = subset(df_counts, treatment == "R"),
               aes(
                 x = .19,
                 xend = .19,
                 y = unique(df_counts$mean[df_counts$treatment=="R"]), 
                 yend = unique(df_counts$mean[df_counts$treatment=="R*"])), 
               color = "grey", size = .5) +


  geom_segment(data = subset(df_counts, treatment == "R"),
               aes(
                 x = .19,
                 xend = .24,
                 y = unique(df_counts$mean[df_counts$treatment=="R*"]), 
                 yend = unique(df_counts$mean[df_counts$treatment=="R*"])
               ), 
               color = "#785ef0", size = .5) +
  ###
  geom_text(data = subset(df_counts, treatment == "R"),
            aes(
              x = .25,
              y = unique(df_counts$mean[df_counts$treatment=="R*"]-.17), 
            ), 
            label = p2, angle=90, color="darkgrey", size=3, vjust=.5, hjust=1.8)+
  geom_segment(data = subset(df_counts, treatment == "R"),
               aes(
                 x = .25,
                 xend = .25,
                 y = unique(df_counts$mean[df_counts$treatment=="R"]), 
                 yend = unique(df_counts$mean[df_counts$treatment=="C"])), 
               color = "grey", size = .5)+
  geom_segment(data = subset(df_counts, treatment == "R"),
               aes(
                 x = .25,
                 xend = .3,
                 y = unique(df_counts$mean[df_counts$treatment=="C"]), 
                 yend = unique(df_counts$mean[df_counts$treatment=="C"])
               ), 
               color = "#dc267f", size = .5)  +
  
  scale_color_manual(values = c("#dc267f","#ffb000", "#648fff", "#785ef0"))+
  scale_fill_manual(values = c("#dc267f","#ffb000", "#648fff", "#785ef0")) ->plt_2A
plt_2A
#ggsave(plt_2A, filename = "plt1.pdf", width = 6.6*4/5,height = 3, dpi = 1200, units = "in", device='pdf')
```
:::
:::

# Color die evokes curiosity

::: columns
::: column
```{r, count motivation by treatment, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
df %>%
  left_join(read_csv("motivation-annotated.csv", col_types = cols_only(participant.code = col_character(), motivation = col_character())), 
            by = "participant.code") %>%
  select(participant.code, treatment, player.checkmore, motivation) %>%
  filter(!is.na(motivation)) %>%
  left_join(read_csv("totaldist-annotated.csv", col_types = cols()) %>% select(participant.code,type,options_visited), by = "participant.code") -> df_temp

## count by selfreport
df_temp %>%
  filter(player.checkmore == 1) %>%
  select(treatment, motivation) %>%
  mutate(motivation = factor(motivation, levels = c("payoff", "curiosity", "other"))) %>%
  count(treatment, motivation) %>%
  pivot_wider(names_from = treatment, values_from = n) -> df_self

df_self  %>%
  mutate_all(funs(ifelse(is.na(.), 0, .))) %>%
  mutate(total = rowSums(pick(where(is.numeric), -motivation)))-> df_self

## count by trajectories
df_temp %>%
  filter(options_visited > 1) %>%
  select(treatment, motivation) %>%
  count(treatment, motivation) %>%
  group_by(treatment) %>%
  mutate(perc = round((n / sum(n)) * 100), digits=0) %>%
  ungroup() %>%
  select(!n) %>%
  pivot_wider(names_from = treatment, values_from = perc) %>%
  select(!digits)->df_traj
```
  
```{r irr, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
library(irr)

read_csv("motivation-annotated.csv", 
         col_types = cols_only(motivation_Carina = col_character(),
                               motivation_Alex = col_character()))%>%
  filter(!is.na(motivation_Alex))-> df_motivation
irr_result <- kappa2(df_motivation)
```
  
As part of the experimental procedure, we elicited individual motivations behind exploring multiple options. 
In particular, the two authors independently classified these self-reports as either \curiosity{} or \payoff{} (Cohen's $\kappa=$ `r round(irr_result$value, digits=1)`, p-value=  `r round(irr_result$p.value, digits=3)`). 
Overall, 36 participants stated to have checked more than one option.   

```{r, prop test, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE}  
df_temp %>% 
  filter(player.checkmore==1) %>% 
  mutate(motivation=ifelse(motivation=="curiosity",1,0)) %>%
  na.omit() %>%
  select(treatment, motivation)->df_prop

prop.test(c(sum(df_prop %>% filter(treatment=="C"|treatment=="C*") %>% pull(motivation)), 
            sum(df_prop %>% filter(treatment=="R"|treatment=="R*") %>% pull(motivation))), 
          c(length(df_prop %>% filter(treatment=="C"|treatment=="C*") %>% pull(motivation)), 
            length(df_prop %>% filter(treatment=="R"|treatment=="R*") %>% pull(motivation))), 
)->p1

prop.test(c(sum(df_prop %>% filter(treatment=="C") %>% pull(motivation)), 
            sum(df_prop %>% filter(treatment=="C*") %>% pull(motivation))), 
          c(length(df_prop %>% filter(treatment=="C") %>% pull(motivation)), 
            length(df_prop %>% filter(treatment=="C*") %>% pull(motivation))), 
          alternative = "greater"
)->p2

prop.test(c(sum(df_prop %>% filter(treatment=="R") %>% pull(motivation)), 
            sum(df_prop %>% filter(treatment=="R*") %>% pull(motivation))), 
          c(length(df_prop %>% filter(treatment=="R") %>% pull(motivation)), 
            length(df_prop %>% filter(treatment=="R*") %>% pull(motivation))), 
          alternative = "greater"
)->p3
```

There was a significantly higher proportion of participants motivated by curiosity in conditions C/CP than in R/RP (${\chi}^2=$ `r round(p1$statistic, digits=1)`, p = `r round(p1$p.value, digits=3)`), which explains the observed difference in the effect time pressure has on reported die rolls.
However, for a given die type, there is no significant effect of time pressure on the distribution of motivations (Color: ${\chi}^2=$ `r round(p2$statistic, digits=1)`, p = `r round(p2$p.value, digits=3)`; Regular: ${\chi}^2=$ `r round(p3$statistic, digits=1)`, p = `r round(p3$p.value, digits=3)`). 
:::

::: column
```{r countypes, cache=TRUE, echo=FALSE,message=FALSE, warning=FALSE}
read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
  filter(participant.code %in% df$participant.code) %>%
  group_by(treatment, type) %>%
  summarise(n = n(), .groups = "drop") %>%
  rename("motivation" = type) %>%
  pivot_wider(names_from = treatment, values_from = n)->df_type

df_type  %>%
  mutate_all(funs(ifelse(is.na(.), 0, .))) %>%
  mutate(total = rowSums(pick(where(is.numeric), -motivation)))->df_type
```
```{r table 1, cache=TRUE, echo=FALSE,message=FALSE, warning=FALSE}
#| label: tbl-1
#| tbl-cap: "Self-reported motivations"
df_self$group <- "Self-report"
df_type$group <- "Trajectory Type"

rbind(df_self,df_type) %>%
  group_by(group) %>%
  gt(rowname_col = "motivation", groupname_col = "group") 
#  gtsave("table.tex")
```
:::
:::

# Mouse cursor trajectories reveal distinct behavioral types

::: columns
::: column
```{r, Fig. 2B, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
df %>%
  left_join(read_csv("motivation-annotated.csv", col_types = cols()), 
            by = "participant.code") %>%
  ungroup() %>%
  filter(!is.na(motivation)) %>%
  mutate(motivation = factor(motivation, levels = c("curiosity","payoff", "other"))) %>%
  select(motivation, player.report_value) ->df_plt

test_2B<-wilcox.test(player.report_value ~ (motivation == "payoff"), data = df_plt, alternative="less")

test_2B <- wilcox.test(df_plt$player.report_value[df_plt$motivation == 'payoff'], mu = 3.5, alternative = "greater")

p_2B = map_pvalue(test_2B$p.value)


df_plt %>%
  ggplot(aes(x = motivation, y = player.report_value))+
  stat_histinterval(breaks = 7,slab_linewidth = 1,interval_alpha = .6, point_alpha=.6, point_size=2) +
  geom_hline(yintercept = 3.5, linetype="dotted", color="darkgrey", size=.2)+
  theme_classic() +
  theme(aspect.ratio = 1)+
  xlab("Motivation") +
  ylab("Reported Value") +
  annotate("text", x = 2, y = 6.7, label = paste("W=", round(test_2B$statistic, digits=1)), color = "black", size = 3,  hjust = 0) +
  annotate("text", x = 2, y = 6.3, label = p_2B, color = "black", size = 3,  hjust = 0)+
  scale_y_continuous(breaks = seq(min(df$player.report_value), max(df$player.report_value), by = 1))->plt_2B
plt_2B
#ggsave(plt_2B, filename = "plt6.pdf", width = 6, height = 6, dpi = 1200, units = "in", device='pdf')
```
:::
::: column
:::
:::

::: columns
::: column
```{r, report-type Fig. 2C, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE}
df %>%
  left_join(read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
              select(participant.code,type),
            by = "participant.code") %>%
  select(participant.code, treatment, player.report_value,type) %>%
  group_by(type) %>%
  mutate(mean = mean(player.report_value)) %>%
  group_by(type, treatment) %>%
  mutate(mean_col=mean(player.report_value)) %>%
  ungroup() ->df_temp_C

df %>%
  left_join(read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
              select(participant.code,type),
            by = "participant.code") %>%
  select(type, player.report_value) %>%
  filter(type=="A<O") %>%
  count(player.report_value) %>%
  pull(n)->observed_outcomes
chisq.test(observed_outcomes, p = rep(1/6, 6))->t_chi
p_temp = map_pvalue(t_chi$p.value)

test_2C<-wilcox.test(player.report_value ~ (type == "A<O"), data = df_temp_C, alternative="less")
p_temp = map_pvalue(test_2C$p.value)

new_labels <- c("A<O" = expression(paste("A<",Omega)),
                "A" = "A",
                "A>O" = expression(paste("A>",Omega)),
                "A=O" = expression(paste("A=",Omega)))

df_temp_C %>%
  ggplot(aes(x = type, y = player.report_value)) +
  stat_histinterval(breaks = 7, slab_linewidth = 1, interval_alpha = .6, point_alpha = .6, point_size = 2) +
  geom_hline(yintercept = 3.5, linetype = "dotted", color = "darkgrey", size = .2) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  xlab("Type") +
  ylab("Reported Value") +
  
  annotate("text", x = 1.6, y = 6.7, label = paste("W=",round(test_2C$statistic, digits=1)),color = "black", size = 3, hjust = 0) +
  annotate("text", x = 1.6, y = 6.3, label = p_temp, color = "black", size = 3, hjust = 0) +
  
  scale_y_continuous(breaks = seq(min(df$player.report_value), max(df$player.report_value), by = 1)) +
  scale_x_discrete(labels = new_labels) -> plt_2C 
plt_2C
#ggsave(plt_2C, filename = "plt6.pdf", width = 6.7847222/4, height = 3, dpi = 1200, units = "in", device='pdf')
```
```{r, arrange fig2, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE}  
ggarrange(plt_2A,
          ggarrange(plt_2B,plt_2C, ncol = 1,labels = c("B", "C")), 
          labels = "A"    
          )->plt_2

ggsave(plt_2, filename = "plt_2.pdf", width = 8, height = 4, dpi = 1200, units = "in", device='pdf')
```
:::
::: column
During the decision stage in the experiment we tracked the individual mouse cursor trajectories. This allows us to classify the participants into four distinct behavioral types based on the initially explored option ($A$) and ultimately reported roll ($\Omega$).
$A<\Omega$ explores multiple options and reports a higher roll than the initial one. Their average reported roll is significantly higher than that of the other types ($W=$ `r round(test_2C$statistic, digits=1)`, $p=$ `r round(test_2C$p.value, digits=3)`, Fig 2C) and we interpret such behavior as dishonest.
:::
:::


::: columns
::: column
```{r, Table 2, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE}  
#| label: tbl-2
#| tbl-cap: "Motivation by behavioral type"
df_temp %>%
  count(type, motivation) %>%
  mutate(motivation = factor(motivation, levels = c("payoff", "curiosity", "other"))) %>%
  pivot_wider(names_from = type, values_from = n, values_fill=0) ->tbl2

tbl2 %>%  
  gt(rowname_col = "motivation") # %>% gtsave("table.tex")

fisher<-fisher.test(tbl2[,2:5])
```
:::
::: column
If we contrast the behavioral types with the aforementioned self-reported motivations (@tbl-2), we can see that types $A\leq\Omega$ are represented mostly by participants motivated by curiosity whereas type $A$ is dominated by those motivated by payoff (Fisher's exact test, simulated p= `r round(fisher$p.value, digits=3)`).
:::
:::


::: columns
::: column
One can also compare our behavioral types to the classification in \cite{Fischbacher08} who use the categories of honest, income maximizers and partial liars to describe their participants. Following their identification strategy, our types $A$ and $A=\Omega$ would correspond to honest, $A<\Omega$ participants with reports lower than 6 would correspond to partial liars and $A<\Omega$ participants reporting 6 would correspond to `income maximizers'.Our estimates suggest that the share of honest participants is considerably higher than reported before (@tbl:3).
:::
::: column
```{r Table 3, cache=TRUE, echo=FALSE}
#| label: tbl-3
#| tbl-cap: "Percentages of reporting types identified by rules of probability or based on mouse trajectories."

## definition by fischbacher
#(1) Honest subjects: The fraction of people reporting a payoff of 1,2,3 is positive.
#(2) Income maximizing subjects: The fraction of people reporting a 6 is above 1/6.
#(3) Partial liars: The fraction of people reporting a 4,5 is above 1/6.

df %>%
  left_join(
    read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
      select(participant.code, type),
    by = "participant.code"
  ) %>%
  select(participant.code, treatment, player.report_value, type) %>%
  #filter(treatment == "C*" | treatment == "C") %>%
  group_by(treatment) %>%
  mutate(n=length(participant.code)) %>%

  summarise(
    honest = sum(player.report_value %in% c(1, 2, 3))/unique(n)*100,
    partial_liar = sum(player.report_value %in% c(4, 5))/unique(n)*100,
    income_max = (sum(player.report_value == 6)/unique(n)+1/6)*6/7*100
  )  -> fisch
fisch$treatment<-"Fischbacher"

### our definition
# honest A, A=O
# income max A<O reporting 6
# partial liar  A<O reporting <6

df %>%
  left_join(
    read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
      select(participant.code, type),
    by = "participant.code"
  ) %>%
  select(participant.code, treatment, player.report_value, type) %>%
 # filter(treatment %in% c("C*", "C")) %>%
  group_by(treatment) %>%
  mutate(n=length(participant.code)) %>%
  group_by(treatment) %>%
  summarise(
    honest = sum(type == "A" | type == "A=O") / unique(n)*100,
    partial_liar = sum(type == "A<O" & player.report_value %in% c(2, 3, 4, 5)) / unique(n)*100,
    income_max = sum(type == "A<O" & player.report_value == 6) / unique(n)*100
  )->hausladen


rbind(fisch, hausladen) %>%
  gt(rowname_col = "treatment") %>%
  fmt_number(columns = c("honest","income_max","partial_liar"), decimals=0) 
  #gtsave("test.tex")

```
:::
:::

# First value visited
```{r}
read_csv('/Users/carinah/Documents/GitHub/color-me-honest/analysis/totaldist-annotated-value.csv') %>%
  na.omit() -> df_temp

observed_frequencies<-table(df_temp$value_first)
expected_frequencies <- rep(length(df_temp$value_first) / 6, 6)
chisq.test(observed_frequencies, p = rep(1/6, 6))

```


# Trajectories provide insights into the dynamics of the decision process
## Initiation Time

::: columns
::: column
```{r time stats, echo=FALSE, cache=TRUE}
# movement time is not normally distributed
df %>%
  mutate(time = sapply(strsplit(as.character(player.mouse_t), ","), function(x) max(as.numeric(x)))) %>%
  inner_join(total_dist, by = c("participant.code" = "participant.code")) %>%
  select(participant.code,treatment,time) %>%
  group_by(treatment) %>%
  summarise(
    mean_tt = mean(time),
    shapiro_tt = shapiro.test(time)$p.value,
    .groups = "drop"
  ) %>% gt() %>% fmt_number(columns = mean_tt:shapiro_tt) -> test_normality
  
# initiation time
df_lng %>%
  group_by(participant.code) %>%
  mutate(changed = c(FALSE, (diff(x) != 0 | diff(y) != 0))) %>%
  filter(changed==TRUE) %>%
  group_by(participant.code, treatment) %>%
  summarise(t=min(t),
            .groups = "drop")  %>%
  ungroup() ->df_temp

df_temp %>%
  do(pairwise_tests = tidy(pairwise.wilcox.test(.$t, .$treatment, p.adj = "none"))) %>%
  unnest(pairwise_tests) %>%
  mutate(signif = map_pvalue(p.value))->init_t

test_C<-wilcox.test(t ~ (treatment == "C"), data = df_temp%>% filter(treatment=="C"|treatment=="C*"), alternative="less")
test_R<-wilcox.test(t ~ (treatment == "R*"), data = df_temp%>% filter(treatment=="R"|treatment=="R*"), alternative="two.sided")
test_p<-wilcox.test(t ~ (treatment == "R*"), data = df_temp%>% filter(treatment=="R*"|treatment=="C*"), alternative="two.sided")
```
```{r Fig 3A, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
df_lng %>%
  group_by(participant.code) %>%
  mutate(changed = c(FALSE, (diff(x) != 0 | diff(y) != 0))) %>%
  filter(changed==TRUE) %>%
  group_by(participant.code, treatment) %>%
  summarise(t=min(t), .groups = "drop") %>%
  
  ggplot(aes(x = treatment, y = t, color=treatment)) +
  stat_dotsinterval(quantiles = 100, fatten_point=1.5, interval_alpha=.9)+
  theme_classic()+
  ylim(0,1)+
  ylab("Initiation Time")+xlab("Treatment")+
  theme(aspect.ratio = 1,
        text=element_text(size=9),
        legend.position = "none")+
  
  ggpubr::geom_bracket(aes(xmin = as.character(init_t[1,1]),xmax = as.character(init_t[1,2]), y.position = .95,label = as.character(init_t[1,4])), data = init_t,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  ggpubr::geom_bracket(aes(xmin = as.character(init_t[3,1]),xmax = as.character(init_t[3,2]), y.position = .85,label = as.character(init_t[3,4])), data = init_t,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  ggpubr::geom_bracket(aes(xmin = as.character(init_t[5,1]),xmax = as.character(init_t[5,2]), y.position = .75,label = as.character(init_t[5,4])), data = init_t,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  ggpubr::geom_bracket(aes(xmin = as.character(init_t[4,1]),xmax = as.character(init_t[4,2]), y.position = .65,label = as.character(init_t[4,4])), data = init_t,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  
  scale_color_manual(values = c("#dc267f","#ffb000", "#648fff", "#785ef0")) ->plt_3A
plt_3A
#ggsave(p4, filename = "plt5.pdf", width = 6.6/4, height= 6/4, dpi = 1200, units = "in", device='pdf')
```
:::
::: column
Concerning initiation time, we find significant differences between the treatments. 
The average initiation time in C is higher than in CP ($W =$ `r round(test_C$statistic, digits=1)`, $p=$ `r round(test_C$p.value, digits=3)`). 
However, there is no difference between R and RP  ($W =$ `r round(test_R$statistic, digits=1)`, $p=$ `r round(test_R$p.value, digits=3)`). 
On the other hand, the average initiation time in R* is higher than in C*  ($W =$ `r round(test_p$statistic, digits=1)`, $p=$ `r round(test_p$p.value, digits=3)`). 
This implies that reporting the die roll was easiest in C* and most difficult in C (Fig 3A). 
:::
:::

::: columns
::: column
```{r Fig 3B, echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE}
df_lng %>%
  group_by(participant.code) %>%
  mutate(changed = c(FALSE, (diff(x) != 0 | diff(y) != 0))) %>%
  filter(changed == TRUE) %>%
  group_by(participant.code, treatment, report) %>%
  summarise(t=min(t),
            .groups = "drop")->df_temp


test_rv<-wilcox.test(t ~ (report == 4), data = df_temp, alternative="less")
p_2B = map_pvalue(test_rv$p.value)


df_lng %>%
  group_by(participant.code) %>%
  mutate(changed = c(FALSE, (diff(x) != 0 | diff(y) != 0))) %>%
  filter(changed == TRUE) %>%
  group_by(participant.code, treatment, report) %>%
  summarise(t=min(t),
            .groups = "drop")  %>%
  mutate(mean_global=mean(t)) %>%
  group_by(report) %>%
  mutate(mean=mean(t)) %>%
  
  group_by(treatment,report) %>%
  mutate(mean_treat=mean(t)) %>%
  
  
  ggplot(aes(y=t, x=factor(report))) +
  geom_point(pch=".", alpha=.8) +
  geom_point(aes(y=mean, x=factor(report)), size=2, color="black") +
  geom_point(aes(y=mean_treat, x=factor(report), color=treatment), size=1.5, shape=18) +
  theme_classic() +
  ylim(0,.82) + 
  xlab("Reported Value") +ylab("Initiation Time")+
  geom_vline(xintercept = 3.5, linetype="dotted", color="grey")+
  annotate("text",x=4,y=.815,label=p_2B, size=3)+
  theme(aspect.ratio = 1, 
        text=element_text(size=9),
        legend.position = "none",
        legend.box = "horizontal",
        legend.direction = "horizontal") +
  scale_color_manual(values = c("#dc267f","#ffb000", "#648fff", "#785ef0")) ->plt_3B
plt_3B
#ggsave(plt_3B, filename = "plt5.pdf", width = 6.6/4, height= 6.6/4, dpi = 1200, units = "in", device='pdf')
```
:::
::: column
We also note a number of interesting findings across all four treatments. Reporting a roll of 4 is associated with the highest initiation time relative to all other reports combined (W=`r round(test_rv$statistic, digits=1)`, p-value= `r round(test_rv$p.value, digits=3)`).
This can be explained by individuals engaging in partial lying under the hypothesis that telling the truth and lying fully both require less effort.
:::
:::


::: columns
::: column
```{r Fig 3C, echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE}
df_lng %>%
  group_by(participant.code) %>%
  mutate(changed = c(FALSE, (diff(x) != 0 | diff(y) != 0))) %>%
  filter(changed==TRUE) %>%
  group_by(participant.code, treatment) %>%
  summarise(t=min(t),
            .groups = "drop")  %>%
  left_join(read_csv("totaldist-annotated.csv", show_col_types = FALSE), 
            by="participant.code") ->df_temp

test_3Cless<-wilcox.test(t ~ (type == "A<O"), data = df_temp, alternative="less")

test_3C<-wilcox.test(t ~ (type == "A=O"), data = df_temp, alternative="less")
p_3C = map_pvalue(wilcox.test(t ~ (type == "A=O"), data = df_temp, alternative="less")$p.value)

new_labels <- c("A<O" = expression(paste("A<",Omega)),
                "A" = "A",
                "A>O" = expression(paste("A>",Omega)),
                "A=O" = expression(paste("A=",Omega)))


df_temp %>%
  group_by(type) %>%
  mutate(mean=mean(t)) %>%
  
  ggplot(aes(y=t, x=reorder(type,mean))) +
  geom_point(pch=".", alpha=.8) +
  geom_point(aes(y=mean, x=factor(type)), size=2, color="black") +
  theme_classic() +
  ylim(0,.8) + 
  xlab("Type") +ylab("Initiation Time")+
  annotate("text",x=3.8,y=.7,label=p_3C, size=3)+
  theme(aspect.ratio = 1, 
        text=element_text(size=9),
        legend.position = "bottom") +
  scale_x_discrete(labels = new_labels)->plt_3C
plt_3C
#ggsave(p3C, filename = "plt5.pdf", width = 6.6/4, height= 6.6/4, dpi = 1200, units = "in", device='pdf')
```
:::
::: column
The $A=\Omega$ type exhibits the highest initiation time relative to all other types combined (W=`r round(test_3C$statistic, digits=1)`, p-value= `r round(test_3C$p.value, digits=3)`). 
On the other hand, the $A<\Omega$ type is not statistically different from the rest (W=`r round(test_3Cless$statistic, digits=1)`, p-value= `r round(test_3Cless$p.value, digits=3)`). 
The pattern implies that it takes more effort to be honest, and it may as well have turned out to be the other way around.
:::
:::

::: columns
::: column
```{r Fig 3D, echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE}
df_lng %>%
  group_by(participant.code) %>%
  mutate(changed = c(FALSE, (diff(x) != 0 | diff(y) != 0))) %>%
  filter(changed==TRUE) %>%
  group_by(participant.code, treatment) %>%
  summarise(t=min(t),
            .groups = "drop")  %>%
  left_join(read_csv("motivation-annotated.csv", col_types = cols()), 
            by = "participant.code") %>%
  select(participant.code, treatment,motivation,t) %>%
  na.omit() %>%
  group_by(motivation) %>%
  mutate(mean=mean(t)) ->df_temp

test_3D<-wilcox.test(t ~ (motivation == "curiosity"), data = df_temp, alternative="less")
p_3D = map_pvalue(test_3D$p.value)

  
ggplot(df_temp, aes(y=t, x=reorder(motivation,mean))) +
  geom_point(pch=".", alpha=.8) +
  geom_point(aes(y=mean, x=factor(motivation)), size=2, color="black") +
  theme_classic() +
  ylim(0,.8) + 
  ylab("")+ 
  xlab("Annotation") +ylab("Initiation Time")+
  annotate("text",x=2,y=.8,label=p_3D, size=3)+
  theme(aspect.ratio = 1, 
        axis.text.x = element_text(vjust = 1.1, hjust=1, size=6),
        legend.position = "bottom") ->plt_3D
plt_3D
#ggsave(plt_3D, filename = "plt5.pdf", width = 6.6,height = 3, dpi = 1200, units = "in", device='pdf')
```
:::
::: column
Between the two motivations to explore reported by the participants, curiosity is associated with a higher initiation time than payoff (W=`r round(test_3D$statistic, digits=1)`, p-value= `r round(test_3D$p.value, digits=3)`), which is to be expected.
:::
:::


## AUC
::: columns
::: column
```{r Fig 3E AUC, echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE}
library(pracma)
source("remapping.R")

df_lng_rot %>% # only A types
  left_join(df%>% select(participant.code, player.report_value), by="participant.code") %>%
  mutate(y_new=abs(y_new)) %>% #otherwise there is negative AUC which makes no sense
  
  group_by(treatment,participant.code) %>%
  summarise(auc = trapz(x_new, y_new)) %>%
  
  ungroup() %>%
  mutate(auc = (auc - min(auc)) / (max(auc) - min(auc))) %>%
  
  group_by(treatment) %>%
  mutate(mean_auc=mean(auc)) ->df_temp


df_temp %>%
  select(participant.code, treatment, auc) %>%
  unique() %>% 
  ungroup() %>%
  do(pairwise_tests = tidy(pairwise.wilcox.test(.$auc, .$treatment, p.adj = "none"))) %>%
  unnest(pairwise_tests)%>% 
  mutate(signif = map_pvalue(p.value)) %>%
  filter(!signif=="ns")-> test_3E

test1 <- wilcox.test(auc ~ treatment, alternative = "less",
                     data = df_temp %>% filter(treatment %in% c("R", "R*")))

ggplot(df_temp, aes(x = treatment, y = auc, color=treatment)) +
  stat_dotsinterval(quantiles = 100, fatten_point=1.5, interval_alpha=.9)+
  theme_classic()+
  theme(aspect.ratio = 1, 
        legend.position = "none",
        text = element_text(size=9)) +
  ylim(0,.75)+xlab("Treatment")+ylab("AUC")+
  scale_color_manual(values = c("#dc267f","#ffb000", "#648fff", "#785ef0"))+
  ggpubr::geom_bracket(aes(xmin = as.character(test_3E[1,1]),
                           xmax = as.character(test_3E[1,2]), 
                           y.position = .7,
                           label = as.character(test_3E[1,4])), 
                       data = test_3E,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
    
  ggpubr::geom_bracket(aes(xmin = as.character(test_3E[2,1]),
                           xmax = as.character(test_3E[2,2]), 
                           y.position = .6,
                           label = as.character(test_3E[2,4])), 
                       data = test_3E,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  ggpubr::geom_bracket(aes(xmin = as.character(test_3E[3,1]),
                           xmax = as.character(test_3E[3,2]), 
                           y.position = .5,
                           label = as.character(test_3E[3,4])), 
                       data = test_3E,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) ->plt_3E
plt_3E
```
:::
::: column
The average area under the curve (AUC) is significantly larger in R* than in R (W=`r round(test1$statistic, digits=1)`, p-value= `r round(test1$p.value, digits=3)`), which indicates a greater level of response conflict in the decision-making process.
:::

:::

## Velocity
::: columns
::: column
```{r Fig 3F velocity, echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE}
df_lng %>%
  left_join(read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
              select(!treatment),
            by="participant.code") %>%
  filter(type=="A") %>%
  filter(!participant.code=="zx7qzgja") %>%
  
  arrange(participant.code, t) %>%
  group_by(participant.code, treatment, report) %>%
  mutate(x2 = lead(x),
         y2 = lead(y),
         t2 = lead(t)) %>%
  ungroup() %>%
  filter(!is.na(x2)) %>%
  
  mutate(distance = sqrt((x2 - x)^2 + (y2 - y)^2),
         time_interval = t2 - t,
         velocity = distance / time_interval) %>%
  
  select(participant.code, treatment, report, t, velocity)-> df_vel
 
# df_vel %>% write_csv("/Users/carinaines/df_vel.csv")
  
  
  df_vel %>%
    group_by(treatment,report, participant.code) %>%
    summarise(velocity=max(velocity), .groups="drop") %>%
    ungroup() %>%
    mutate(velocity = (velocity - min(velocity)) / (max(velocity) - min(velocity))) ->df_temp
  
  
df_temp %>%
  select(participant.code, treatment, velocity) %>%
  unique() %>% 
  ungroup() %>%
  do(pairwise_tests = {
    tests <- pairwise.wilcox.test(.$velocity, .$treatment, p.adj = "none")
    tests_results <- tidy(tests)
    tests_results <- tests_results %>% add_column(TestStatistic = tests$statistic)
    tests_results
  }) %>%
  unnest(pairwise_tests) %>%
  mutate(signif = map_pvalue(p.value)) %>%
  filter(!signif=="ns")-> test_3F
  
test1 <- wilcox.test(velocity ~ treatment, alternative = "less",
                     data = df_temp %>% filter(treatment %in% c("R", "R*")))

  ggplot(df_temp, aes(x = treatment, y = velocity, color=treatment)) +
    stat_dotsinterval(quantiles = 100, fatten_point=1.5, interval_alpha=.9)+
    theme_classic()+
    theme(aspect.ratio = 1,
          legend.position = "none",
          text = element_text(size=9)) +
    xlab("Treatment")+ ylab("Max Velocity") + ylim(0,.75)+
    scale_color_manual(values = c("#dc267f","#ffb000", "#648fff", "#785ef0")) +

ggpubr::geom_bracket(aes(xmin = as.character(test_3F[1,1]),
                         xmax = as.character(test_3F[1,2]), 
                         y.position = .6,
                         label = as.character(test_3F[1,4])), 
                     data = test_3F,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  
ggpubr::geom_bracket(aes(xmin = as.character(test_3F[2,1]),
                         xmax = as.character(test_3F[2,2]), 
                         y.position = .5,
                         label = as.character(test_3F[2,4])), 
                     data = test_3F,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
ggpubr::geom_bracket(aes(xmin = as.character(test_3F[3,1]),
                         xmax = as.character(test_3F[3,2]), 
                         y.position = .7,
                         label = as.character(test_3F[3,4])), 
                     data = test_3F,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) ->plt_3F
plt_3F
```
:::
::: column
Furthermore, the $R*$ group displayed greater peak (maximum) velocity than the $R$ group, indicating a greater level of commitment, vigor, and impulsiveness for action \cite{yamauchi2019assessing} (W=`r round(test1$statistic, digits=1)`, p-value= `r round(test1$p.value, digits=3)`).
:::
:::

## Idle and Movement Time

::: columns
::: column
```{r Fig 3G idle , cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
df_lng %>%
    left_join(read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
              select(!treatment),
            by="participant.code") %>%
  filter(type=="A") %>%
  
  group_by(treatment, participant.code) %>%
  summarise(
    changed = c(FALSE, (diff(x) != 0 | diff(y) != 0)),
    first_change = min(t[changed]),
    total_time = max(t),
    idle_time_with = total_time - sum(diff(t[changed])),
    idle_time = total_time - (first_change - t[1]) - sum(diff(t[changed & t >= first_change]))
  ) %>%
  ungroup() %>%
  select(participant.code, treatment, idle_time) %>%
  distinct() %>%
  do(pairwise_tests = tidy(pairwise.wilcox.test(.$idle_time, .$treatment, p.adj = "none"))) %>%
  unnest(pairwise_tests) %>%
  mutate(signif = map_pvalue(p.value)) %>%
  filter(!signif=="ns")-> test_3G

  
df_lng %>%
    left_join(read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
             select(!treatment),
             by="participant.code") %>%
  filter(type=="A") %>%
  group_by(participant.code) %>%
  mutate(
    changed = c(FALSE, (diff(x) != 0 | diff(y) != 0)),
    first_change = min(t[changed]),
    total_time = max(t),
    idle_time_with = total_time - sum(diff(t[changed])),
    idle_time = total_time - (first_change - t[1]) - sum(diff(t[changed & t >= first_change]))
  ) %>%
  ungroup() %>%
  select(participant.code, treatment, idle_time) %>%
  unique() %>%
  
  ggplot(aes(x = treatment, y = idle_time, color=treatment)) +
  stat_dotsinterval(quantiles = 100, fatten_point=1.5, interval_alpha=.9)+
  theme_classic()+
  ylim(0,1)+
  ylab("Idle Time")+xlab("Treatment")+
  theme(aspect.ratio = 1, 
        legend.position = "none",
        text=element_text(size=9))+
  scale_color_manual(values = c("#dc267f","#ffb000", "#648fff", "#785ef0")) +
  
ggpubr::geom_bracket(aes(xmin = as.character(test_3G[1,1]),
                         xmax = as.character(test_3G[1,2]), 
                         y.position = .6,
                         label = as.character(test_3G[1,4])), 
                     data = test_3G,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  
ggpubr::geom_bracket(aes(xmin = as.character(test_3G[2,1]),
                         xmax = as.character(test_3G[2,2]), 
                         y.position = .5,
                         label = as.character(test_3G[2,4])), 
                     data = test_3G,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
ggpubr::geom_bracket(aes(xmin = as.character(test_3G[3,1]),
                         xmax = as.character(test_3G[3,2]), 
                         y.position = .7,
                         label = as.character(test_3G[3,4])), 
                     data = test_3G,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) ->plt_3G
plt_3G
```
```{r Fig 3H movement, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
df %>%
  left_join(read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
             select(!treatment),
             by="participant.code") %>%
  filter(type=="A") %>%
  mutate(time = sapply(strsplit(as.character(player.mouse_t), ","), function(x) max(as.numeric(x)))) %>%
  select(treatment, time) ->df_temp
df_temp %>%  do(pairwise_tests = tidy(pairwise.wilcox.test(.$time, .$treatment, p.adj = "none"))) %>%
  unnest(pairwise_tests)%>% 
  mutate(signif = map_pvalue(p.value)) %>%
  filter(!signif=="ns")-> test_3H

test1 <- wilcox.test(time ~ treatment, alternative = "greater",
                     data = df_temp %>% filter(treatment %in% c("R", "R*")))


df %>%
  left_join(read_csv("totaldist-annotated.csv", show_col_types = FALSE) %>%
             select(!treatment),
             by="participant.code") %>%
  ungroup() %>%
  filter(type=="A") %>% #why did I filter by those?
  group_by(participant.code) %>%
  mutate(time = sapply(strsplit(as.character(player.mouse_t), ","), function(x) max(as.numeric(x))))   %>%

  ggplot(aes(x = treatment, y = time, color=treatment)) +
  stat_dotsinterval(quantiles = 100, fatten_point=1.5, interval_alpha=.9)+
  theme_classic()+
  ylim(1,6)+
  ylab("Movement Time")+xlab("Treatment")+
  theme(aspect.ratio = 1, 
        legend.position = "none",
        text=element_text(size=9))+
  scale_color_manual(values = c("#dc267f","#ffb000", "#648fff", "#785ef0")) +

ggpubr::geom_bracket(aes(xmin = as.character(test_3H[1,1]),
                         xmax = as.character(test_3H[1,2]), 
                         y.position = 5,
                         label = as.character(test_3H[1,4])), 
                     data = test_3H,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  
ggpubr::geom_bracket(aes(xmin = as.character(test_3H[2,1]),
                         xmax = as.character(test_3H[2,2]), 
                         y.position = 4.5,
                         label = as.character(test_3H[2,4])), 
                     data = test_3H,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
ggpubr::geom_bracket(aes(xmin = as.character(test_3H[3,1]),
                         xmax = as.character(test_3H[3,2]), 
                         y.position = 5.5,
                         label = as.character(test_3H[3,4])), 
                     data = test_3H,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  
ggpubr::geom_bracket(aes(xmin = as.character(test_3H[4,1]),
                         xmax = as.character(test_3H[4,2]), 
                         y.position = 4,
                         label = as.character(test_3H[4,4])), 
                     data = test_3H,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) +
  
ggpubr::geom_bracket(aes(xmin = as.character(test_3H[5,1]),
                         xmax = as.character(test_3H[5,2]), 
                         y.position = 5,
                         label = as.character(test_3H[5,4])), 
                     data = test_3H,size=.1,inherit.aes = FALSE, tip.length =c(.01,.01),label.size = 2.5) ->plt_3H
plt_3H
```
:::
::: column
Note that for the subsequent analysis I only use types A. 
At the same time, the former exhibit a significantly lower overall mouse movement time than the latter  (W=`r round(test1$statistic, digits=1)`, p-value= `r round(test1$p.value, digits=3)`) without any difference in idle time.
:::
:::

```{r, Fig 3, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE}  
ggarrange(
  plt_3A, plt_3B,plt_3C,plt_3D,
  plt_3E, plt_3F,plt_3G,plt_3H,
  labels = c("A", "B", "C", "D", "E", "F", "G", "H"),
  ncol = 2,
  nrow=4) ->plt_3

ggsave(plt_3, filename = "plt_3.pdf", width = 6.7847222, height = 3.5, dpi = 1200, units = "in", device='pdf')
ggsave(plt_3, filename = "plt_3_1.pdf", width = 6, height = 12, dpi = 1200, units = "in", device='pdf')
```


\setcounter{table}{0}
\renewcommand{\thetable}{A.\arabic{table}}

# Appendix 

```{r A.1, cache=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
#| label: tbl-A1
#| tbl-cap: "Data Sample Overview"
data <- tibble(
  'Jena' = c(
    dim(raw_nov)[1],
    length(unique(raw_nov$session.code)),
    table(raw_nov$player.cblind)[2],
    table(raw_nov$player.report)[7],
    round(table(raw_nov$player.sex)[1] / sum(table(raw_nov$player.sex))*100, digits=0),
    round(mean(raw_nov$player.age), digits=1)
  ),
  'Bonn' = c(
    dim(raw_jun)[1],
    length(unique(raw_jun$session.code)),
    table(raw_jun$player.cblind)[2],
    table(raw_jun$player.report)[7],
    round(table(raw_jun$player.sex)[1] / sum(table(raw_jun$player.sex))*100, digits=0),
    round(mean(raw_jun$player.age), digits=1)
  )
) %>% 
  mutate(`overall` = case_when(
    row_number() %in% c(5, 6) ~ (`Jena` + `Bonn`) / 2, 
    TRUE ~ `Jena` + `Bonn`
  ))
  
data$name<-c('observations', 'sessions', 'cblind', 'failed', '% females', 'mean age')
data %>%  gt(rowname_col = "name") 
```

```{r A.2, cache=TRUE, echo=FALSE}
#| label: tbl-A2
#| tbl-cap: "Time Pressure Manipulation Check"

test1 <- wilcox.test(player.recall_pressure ~ treatment, alternative = "less",
                     data = df %>% filter(treatment %in% c("R", "R*")))
test2 <- wilcox.test(player.recall_pressure ~ treatment, alternative = "less",
                     data = df %>% filter(treatment %in% c("C", "C*")))
test3 <- wilcox.test(player.recall_pressure ~ treatment, alternative = "two.sided",
                     data = df %>% filter(treatment %in% c("R*", "C*")))

test4 <- wilcox.test(player.recall_tpressure ~ treatment, alternative = "less",
                     data = df %>% filter(treatment %in% c("R", "R*")))
test5 <- wilcox.test(player.recall_tpressure ~ treatment, alternative = "less",
                     data = df %>% filter(treatment %in% c("C", "C*")))
test6 <- wilcox.test(player.recall_tpressure ~ treatment, alternative = "two.sided",
                     data = df %>% filter(treatment %in% c("R*", "C*")))

test7 <- wilcox.test(player.recall_speed ~ treatment, alternative = "less",
                     data = df %>% filter(treatment %in% c("R", "R*")))
test8 <- wilcox.test(player.recall_speed ~ treatment, alternative = "less",
                     data = df %>% filter(treatment %in% c("C", "C*")))
test9 <- wilcox.test(player.recall_speed ~ treatment, alternative = "two.sided",
                     data = df %>% filter(treatment %in% c("R*", "C*")))

group1 <- c("R", "C", "R*")
group2 <- c("R*", "C*", "C*")
test <- c("less", "less", "two.sided")
W <- c(test1$statistic, test2$statistic, test3$statistic)
p.value <- c(test1$p.value, test2$p.value, test3$p.value)

W2 <- c(test4$statistic, test5$statistic, test6$statistic)
p.value2 <- c(test4$p.value, test5$p.value, test6$p.value)

W3 <- c(test7$statistic, test8$statistic, test9$statistic)
p.value3 <- c(test7$p.value, test8$p.value, test9$p.value)

tbl <- tibble(
  group1 = group1,
  group2 = group2,
  test = test,
  W = W,
  p.value = p.value,
  
  W2 = W2,
  p.value2 = p.value2,
  
  W3 = W3,
  p.value3 = p.value3
)

tbl %>%
  gt(rowname_col = "group1") %>%
  tab_spanner(label = "Pressure", columns = c(W, p.value)) %>%
  tab_spanner(label = "D-Pressure", columns = c(W2, p.value2)) %>%
  tab_spanner(label = "Speed", columns = c(W3, p.value3)) %>%
  tab_header(title = "Test Results") %>%
  cols_align(align = "center", columns = everything()) %>%
  cols_label(group1 = "Group 1", group2 = "Group 2", test = "Test", 
             W = "W", p.value = "P-value")%>%
  fmt_number(columns = c(p.value, p.value2, p.value3), decimals = 2) %>%
  fmt_number(columns = c(W, W2, W3), decimals = 0) 
#  gtsave("test.tex")
```


::: columns
::: column
```{r A.3, cache=TRUE, echo=FALSE}
#| label: tbl-A3
#| tbl-cap: "Participants Favorite Color"
df_counts <- as.data.frame(table(df$player.favcolor))
colnames(df_counts)<-c('color', 'count')
df_counts$color<-c("blue", "green", "brown", "pink", "yellow", "grey", "none")
df_counts$color <- factor(df_counts$color, levels = df_counts$color)
df_counts %>% gt()

# report = favcolor?
t<-table(ifelse(df$player.favcolor[ c(df$treatment=="C" | df$treatment== "C*")]==df$player.report_face[ c(df$treatment=="C" | df$treatment== "C*")],1,0))
share_favcol<-t[2]/sum(t) 

bt<-binom.test(t[2], sum(t), p = 1/6)
success<-round(bt$statistic/bt$parameter*100, digits=3)
```
:::
::: column
We found that mouse movements are unlikely to be driven by other factors than the payoff related to the color. To control for possible other motives for a participant's choice of color, we asked them to report their favorite color. Only `r success` % of the participants reported their favorite color. A binomial test shows that the probability of success (favorite colors reported) is not significantly different from a random choice (p-value = `r round(bt$p.value, digits=3)`).
:::
:::

```{r A.4, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
#| label: tbl-A4
#| tbl-cap: "CRT"
df_summary <- df %>%
  mutate(`bat and ball` = ifelse(player.crt1 == 5, 1, 0), 
         `machine` = ifelse(player.crt2 == 100, 1, 0), 
         `lily pads` = ifelse(player.crt3 == 47, 1, 0)) %>% 
  pivot_longer(cols = c(`bat and ball`, machine, `lily pads`), names_to = "CRT", values_to = "Correct") %>%
  group_by(treatment, CRT) %>%
  summarize(
    correct_count = sum(Correct),
    total_count = n(),
    .groups = 'drop'
  )


df_summary %>%
  split(.$CRT) %>%
  map_dfr(~{
    test_result <- chisq.test(.$correct_count, .$total_count - .$correct_count)
    data.frame(
      CRT = unique(.$CRT),
      Chi_Square = test_result$statistic,
      df = test_result$parameter,
      p_value = test_result$p.value
    )
  }) %>% 
  gt() %>%
  fmt_number(
    columns = p_value,
    decimals = 2
  ) #%>% gtsave("test.tex", inline_css = TRUE)
```


```{r A.41, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

df %>%
  mutate(`bat and ball` = ifelse(player.crt1 == 5, 1, 0), 
         `machine` = ifelse(player.crt2 == 100, 1, 0), 
         `lily pads` = ifelse(player.crt3 == 47, 1, 0)) %>%
  group_by(participant.code)%>%
  mutate(correct=sum(`bat and ball`, `machine`,`lily pads`)) %>%
  left_join(read_csv("totaldist-annotated.csv", col_types = cols()), 
            by = "participant.code") %>%
    select(participant.code, type, correct)-> df_temp
df_temp%>%  group_by(type) %>%
  count(correct) %>%
  pivot_wider(names_from = correct, values_from = n)->tbl

tbl[is.na(tbl)] <- 0
print(fisher.test(tbl[,2:5], workspace = 2e8))
print(chisq.test(tbl[,2:5]))

kruskal_result <- kruskal.test(correct ~ type, data = df_temp)
print(kruskal_result)

```


::: columns
::: column
```{r A.5, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE, message=FALSE}  
#| label: tbl-A5
#| tbl-cap: "Percentage of participants who have checked more than one option"
df %>%
  select(participant.code, treatment, player.checkmore) %>%
  na.omit() %>%
  left_join(read_csv("totaldist-annotated.csv", col_types = cols()) %>%
              select(participant.code, options_visited), 
            by = "participant.code") %>%
  mutate(options_visited = ifelse(options_visited > 1, 1, 0)) %>%
  rename("self-reported" = player.checkmore,
         "trajectories" = options_visited) -> df_temp


df_temp %>%
  pivot_longer(cols = c(`self-reported`, `trajectories`)) %>%
  group_by(treatment, name) %>%
  summarise(value = sum(value)) %>%
  group_by(treatment) %>%
  mutate(percentage = round(value / sum(value) * 100, 0)) %>%
  ungroup() %>%
  select(!value) %>%
  pivot_wider(names_from = treatment, values_from = percentage) %>%
  gt(rowname_col = "name") %>%
  gtsave("table.tex")


# by self-reported motivation
df_temp %>%  
  group_by(treatment) %>%
  summarise(
    total = n(),
    honest = round(sum(`self-reported` == `trajectories`) / n() * 100),
    confusion = round(sum(`self-reported` == 1 & `trajectories` == 0) / n() * 100),
    lie = round(sum(`self-reported` == 0 & `trajectories` == 1) / n() * 100)) %>%
  ungroup() %>%
  select(!total) %>%
  pivot_longer(cols = c(honest, confusion, lie), names_to = "type", values_to = "percentage") %>%
  pivot_wider(names_from = treatment, values_from = percentage) ->df_unused
  #gt(rowname_col = "type")
```
:::

::: column
Participants were asked to self-report whether they checked more than one option. Additionally, mouse trajectories were analyzed to determine the exact number of options checked by each participant. A number on the clock dial was considered checked if the mouse cursor crossed it during the task.
:::
:::

```{r toannotate, cache=TRUE, echo=FALSE, warning=FALSE, echo=FALSE, message=FALSE}  
#this generates the dataset that the authors annotated for motivation
df %>%
  select(participant.code, player.checkmore, player.checkwhy) %>%
  na.omit() %>%
  arrange(player.checkmore) %>%
  filter(!player.checkwhy=="...nun drfen Sie zur Tastatur greifen") %>%
  filter(!player.checkwhy=="") -> to_annotate
  #write.csv("motivation.csv") 
```
